\section*{\textbf{April 16 (Daren)}}

	Today we will talk about index of operators of certain simple form on cylinders, following Kronheimer-Mrowka.
\newline
		
		
		\textbf{Two warnings:}\\
		\begin{enumerate}
			\item Index theory is for linear operators, but we will deal with non-linear operators later. What we want to compute indices of are the linearisations of the non-linear operators at the solutions of the non-linear equations.
			\item Index theory, and more generally Fredholm theory, is generally done in the setting of Hilbert space $W^{k,2}$. \\
			For $J$-holomorphic curve related problems, we will need to use $W^{k,p}$ spaces where $p>2$, for the following reason:
			 \begin{itemize}
			 	\item we need $kp >2$, so that
			 	 \begin{itemize}
			 	 	\item the definition of the relevant completion in this non-linear case requiresthis.
			 	 	\item $W^{k,p}$ is closed under multiplication.
			 	 	\item $W^{k,p}\hookrightarrow C^0$ compactly.
			 	 \end{itemize}
			 	\item k=1, because of elliptic regularity.
			 \end{itemize}
			 Hence, the following results, especially the ones regarding Fredholmness of operators, are not good enough for what we need later.
		\end{enumerate}
		
		\textbf{Quick reminders on Fredholm operators:}
		\vspace{5mm}
		$H_1,H_2$ are Hilbert spaces.
		\begin{itemize}
			\item \textbf{Definition}: A bounded operator $F: H_1\rightarrow H_2$ is called \textit{Fredholm} if its kernel and cokernel are both finite dimensional and it has closed range. The \textit{index} of $F$ is $\text {dim ker}(F) - \text{dim coker}(F)$.
			\item \textbf{Definition}: A bounded operator $F: H_1\rightarrow H_2$ is called \textit{compact} if it is the limit of a sequence of finite rank operators in the operator norm. Equivalently, if it maps bounded set $B$ in $H_1$ to precompact set $F(B)$ in $H_2$.
			 \item 	\textbf{Lemma}: $F: H_1\rightarrow H_2$ is Fredholm if and only if $\exists P: H_1\rightarrow H_2$, such that $PF -id_{H_1}$ and $FP - id_{H_2}$ are compact operators. Such $P$ is called a parametrix of $F$.
			 \item \textbf{Lemma}: If $F_t$ is a continuous family of Fredholm operators for $t\in[0,1]$, then $ind(F_0) = ind(F_1)$.
			
		\end{itemize}
	\vspace{5mm}
		\textbf{Main proposition today:}\\
		\vspace{5mm}
		Let $Y$ be a closed manifold, $Z = \mathbb{R}\times Y$, where $t$ is the coordinate in the $\mathbb{R}$-direction. $E\rightarrow Y $ is a vector bundle, with an Euclidean metric on the fiber. The pullback of $E$ to $Z$ along projection to $Y$ is called $E$ again.
		\vspace*{5mm} 
		
		
		
			\textbf{Proposition 14.2.1}(in Kronheimer-Mrowka): Let $L_0$ be a first-order, self-adjoint elliptic operator acting
			on sections of a vector bundle $E \rightarrow Y$ , and let $h_t$ be a time-dependent bounded
			operator on $L^2(Y,E)$, varying continuously in the operator norm topology
			and equal to constants $h_{\pm}$ on each ends. Suppose $L_0 + h_{\pm}$ are \textit{hyperbolic}. Then the operator
		\[Q = \dfrac{d}{dt} + L_0 + h_{t} : L^2_1(Z,E) \rightarrow L^2(Z,E)\]
			is Fredholm and has index equal to the \textit{spectral flow} of the path of operators
			$L_0+h_t$, where $L^2_1(Z,E) = W^{1,2}(Z,E)$.
			\vspace{5mm}
		
		\textbf{Definition}: An operator $L$ is called \textit{hyperbolic} if it has no eigenvalue on the imaginary axis.\\
		\vspace{5mm}
		\textbf{Definition}: For a family of operators $L_0+h_t$ satisfying the condition in the proposition, the \textit{spectral flow} is defined as the \textbf{net} number of eigenvalues whose real part changing from negative to positive. \\
		\vspace{5mm }To be more precise, first deform the path $L_0 + h_t$ so that it is smooth over $(0,1)$. Then consider the set $S = \{(t,\lambda)\text{ } | \text{ }\lambda \in Spec(L_0+h_t)\}$. By spectrum theory, the spectrum of $L_0+h_t$ is discrete, and the generalized eigenspaces are finite dimensional. (See Lemma 12.2.4 in K-W). We say $(t,\lambda)$ is a \textit{simple point} if the generalized $\lambda$-eigenspace of $L_0+h_t$ is 1-dimensional. At simple points, $S$ is a smooth 1-manifold, on which $t$ is a local coordinate; we use the coordinate $t$ to orient $S$ at such points. In the space of bounded operators on $L_2$, the set of those $h$ for which the spectrum of $L_0+h$ has a non-simple eigenvalue lying on the imaginary axis is a locally finite union of submanifolds of codimension at least 2.(see Lemma 12.2.4 again) The path $h_t$ can therefore be moved so that the intersection of $S$ with $(0, 1)\times i\mathbb{R}$ consists entirely of simple points; and any two such paths can be joined by a homotopy of paths with the same property. For such a path, we define the spectral flow as the intersection number of $S$ with $(0, 1)\times i\mathbb{R}$. From this perspective, we can see the the spectral flow depends only on the starting and ending points $h_{\pm}$. \\
		\vspace{5mm}
		Lemma 12.2.4 in K-W says the following: \\
		\vspace{5mm}
		\textbf{Lemma 12.2.4} If $L=L_0+h:$  $L^2_1(Y,E) \rightarrow L^2(Y,E)$ satisfies the condition in the previous proposition, then 
		\begin{itemize}
		    \item There  are  only  finitely  many  eigenvalues  of  the  complexification  $L\otimes {\mathbb{C}}$ in  any  compact  subset  of  the  complex  plane $\mathbb{C}$,  and  the  generalized  eigenspaces  of  the  complexification  are  finite-dimensional. All  the generalized eigenvectors belong to $L^2_1(Y,E)$.
		    \item If $h$, like $L_0$, is self-adjoint, then the eigenvalues are real, and there is a complete orthonormal system of eigenvectors ${e_n}$in $L^2(Y,E)$. The span of the eigenvectors is dense in $L^2_1(Y,E)$.
		    \item If $h$ is not self-adjoint, the imaginary parts of the eigenvalues $\lambda$ of $L\otimes 1_{\mathbb{C}}$ are bounded by the $L_2$-operator norm of $(h-h^*)/2$.
		\end{itemize}
		\vspace{5mm}
		$\textbf{Proof of the proposition:}$ \\
		\vspace{5mm}
		\textbf{Step 1:} We consider the translational invariant case, $e.g.$ when $h_t=h, \forall t$. In this case, the spectral flow is obviously 0, so we need to show the index of $D$ is 0. Assume $E$ is a complex vector bundle, (for the general case, note that $C^{\infty}(E)$ are the real sections of $C^{\infty}(E\otimes\mathbb{C})$, and the Fourier transform that we will do below sends them to sections that are fixed under some other involution). \\
		\vspace{2mm}
		Let $F_1$ be the completion of $C_c^{\infty}(E\otimes\mathbb{C})$, the space of compactly supported smooth sections of $E\otimes\mathbb{C}$, with respect to the norm \[ \left\lVert \hat{u}\right\rVert^2 = \sum^1_{i=0} \int^{\infty}_{-\infty} \|\xi\|^{2(1-i)} \left\lVert \hat{u}\right\rVert^2_{L^2_1(\{\xi\}\times Y)} d\xi  \]
		
		Consider the Fourier transform of sections of $E\rightarrow \mathbb{R}_t\times Y$ with respect to the $t$-variable. \[\hat{u}(\xi,y) =  \int^{\infty}_{-\infty} e^{-it\xi} u(t,y)dt \]
		The Fourier transform sends $L^2(Z,E) $ to $L^2(Z,E)$, and $L^2_1(Z,E)$ to $F_1$. The Fourier transform of $D= \dfrac{d}{dt} + L_0 + h$ is $\hat{D} = L_0 + h + i\xi$ :    $F_1 \rightarrow L^2(Z,E)$.  We will show $\Hat{D}$ is invertible. \\
		\vspace{5mm} Let's consider what the operator does on each slice first. \\
		Let $\hat{D}_{\xi} = L_0 + h +i\xi : $  $L^2_1(Y,E) \rightarrow L^2(Y,E)$ for $\xi \in \mathbb{R}$. By hyperbolicity of the operator $L_0+h$, $\Hat{D}_{\xi}$ is injective. (This doesn't hold in the general case, where we only know the hyperbolicity at two ends ) Moreover, by standard elliptic theory on closed manifolds, $\hat{D}_{\xi}$ is Fredholm. By invariance of index under deformation, we have ind($\Hat{D}_{\xi}) = $ ind($L_0$), and \begin{align*}
		    \text{ind}(L_0) & = \text{dim Ker}(L_0) - \text{dim Coker}(L_0)  \\
		                    & = \text{dim Ker}(L_0) - \text{dim Ker }(L_0^*)\\
		                    & = \text{dim Ker}(L_0) - \text{dim Ker}(L_0) =0
		\end{align*}
		Therefore, $\Hat{D}_{\xi}$ is invertible. \\
		
		\vspace{5mm} Then, we define the inverse $\hat{D}^{-1}$: $C^{\infty}(Z,E) \rightarrow L^2_{1,loc}(Z,E)$ by applying $(L_0+h+i\xi)^{-1}$  slicewise. We need to give a bound of $F_1$-norm of $(L_0+h+i\xi)^{-1}(f)$ in terms of $L^2$-norm of $f$, so that we can extend it to a bounded operator from $L^2(Z,E) $ to $F_1$. (Check Lemma 14.1.3 in K-W for details) \\ 
		
		\vspace{5mm}
		\textbf{Step 2}: For the general case $D=\dfrac{d}{dt}+h_t+L_0$, we show $D$ is Fredholm first, using the \textit{parametrix gluing technique.} (which is important in index theory)\\
		\vspace{2mm}
	    Choose $a'<a<b<b' $ in $\mathbb{R}$, such that $h(t)=h_-$ for $t<a$, $h(t) = h_+ $  for $t >b$.\\
	    \vspace{2mm}
	    Choose partition of unity $\eta_{\pm} :\mathbb{R} \rightarrow [0,1] $, such that $\eta_-+\eta_+=1$,  $ \eta_-(t) =1$ for $t \leq a$, and $\eta_+(t) = 1$ for $t\geq b $. \\
	    \vspace{2mm}
	    Choose bump functions $\gamma_{\pm}$, such that $\gamma_-(t) = 1 $ for $t \leq b$, and $\gamma_+(t) =0$ for $t \geq b'$. Similarly, $\gamma_+(t)  = 0 $ for $t\leq a'$, and $\gamma_+(t) =1$ for $t \geq a$. \\
	    \newpage
		Let $G_{\pm}: L^2(Z,E) \rightarrow L^2_1(Z,E)$ be the inverse of $D_{\pm}= \dfrac{d}{dt} +L_0+h_{\pm}$ as in Step 1. Define \[P : L^2(Z,E) \rightarrow L^2_1(Z,E) \]\[
		e \text { }\rightarrow \text{ } \gamma_-G_-\eta_-e + \gamma_+G_+\eta_+e\]
		
		Claim: $P$ is a parametrix for $D$.
		Proof: We compute $DP$ explicitly. 
		\begin{align*}
		    DPe = & D(\sum \gamma_{\pm}G_{\pm}\eta_{\pm}e)\; \; \; \; \; \;  \text{       (summing over + and -)} \\
		    & = \sum \gamma'_{\pm}G_{\pm}\eta_{\pm}e + \sum \gamma_{\pm}D(G_{\pm}\eta_{\pm}e) \\
		    & = \sum \gamma'_{\pm}G_{\pm}\eta_{\pm}e +  \sum \gamma_{\pm}(D-D_{\pm})G_{\pm}\eta_{\pm}e + e \;  \; \; \; \text{(As } D_+G_+ = D_-G_- = id\text {, and} \gamma_-\eta_-+\gamma_+\eta_+ =1 )\\
		    & = e + \sum (\gamma'_{\pm}+ \gamma_{\pm}(h-h_{\pm}))G_{\pm}\eta_{\pm}e\\
		\end{align*}
		Therefore $id-DP$ is compact, as the maps $G_{\pm}\eta_{\pm} : \; L^2(Z,E) \rightarrow L^2_1(Z,E) $ are bounded, and $\gamma'_{\pm}+ \gamma_{\pm}(h-h_{\pm})$ factor through $L^2_1(Z,E) \hookrightarrow L^2_c(Z,E)$, which is compact by Rellich embedding theorem.\\
		\vspace{5mm}
		
		We will start with Step 3 in the next lecture, which does the actual computation of index.
		
		
		
		
		
	


% \documentclass[12pt, letterpaper]{article}
% \usepackage[utf8]{inputenc}
% \usepackage{amsmath,amssymb}
% \usepackage[a4paper,margin=2cm]{geometry}
% \usepackage{graphicx}
% \usepackage{verbatim}
% \usepackage{float}
% \usepackage{wrapfig}
% \usepackage{tikz-cd}

% \usepackage{makecell}

% \begin{document}
% 	\title{Lecture 4 Index of certain operators on cylinders}
% 	\date{April 16, 2019}
% 	\maketitle

	
		
% 	\end{document}